---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bluelink

<!-- badges: start -->
[![R-CMD-check](https://github.com/mdsumner/bluelink/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mdsumner/bluelink/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of bluelink is to provide access to the Bluelink Reanalysis (BRAN2023) via NetCDF sources. 


## Bluelink is 

BRAN2023, a 4 dimensional nearly-global ocean product organized by 
 monthly files at 0.1 degree resolution with 51 depth levels ('3600x1500x51x<days>'). 
 The goal of BRAN is to provide a realistic quantitative description of the 
 three-dimensional time-varying ocean circulation of all physical variables 
 (temperature, salinity, sea-level and three components of velocity) for the last 
 few decades. <https://research.csiro.au/bluelink/global/reanalysis/>

## Installation

You can install the development version of bluelink like so:

``` r
remotes::install_github("mdsumner/bluelink")
```

## Example

This is a basic example which shows you how to read the earliest available for this variable. 

```{r example0}
library(bluelink)
read_bluelink(varname = "ocean_w")
```

Other variables sometimes have diferent ranges in times. 

```{r example}
read_bluelink(varname = "ocean_temp")
```

We can give a particular date. 

```{r example2}
read_bluelink("2023-12-31", varname = "ocean_temp")
```

Generally, take the year you are in and you should be able to get days from last year. 


## Try a time series

Every day on the first of September

```{r time}
dts <- seq(as.Date("2010-01-01"), as.Date("2023-10-10"), by = "1 year")

options(parallelly.fork.enable = TRUE, future.rng.onMisuse = "ignore")
library(furrr); plan(multicore)

sst <- future_map_dbl(dts, \(.x) terra::extract(read_bluelink(.x, varname = "ocean_temp"), cbind(150, -42))[[1]])
plan(sequential)
plot(dts, sst)

```

## Code of Conduct
  
Please note that the bluelink project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
