---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bluelink

<!-- badges: start -->
<!-- badges: end -->

The goal of bluelink is to provide access to the Bluelink Reanalysis (BRAN2020) via NetCDF sources. 


## Bluelink is 

BRAN2020, a 4 dimensional nearly-global ocean product organized by 
 monthly files at 0.1 degree resolution with 51 depth levels ('3600x1500x51x<days>'). 
 The goal of BRAN is to provide a realistic quantitative description of the 
 three-dimensional time-varying ocean circulation of all physical variables 
 (temperature, salinity, sea-level and three components of velocity) for the last 
 few decades. <https://research.csiro.au/bluelink/global/reanalysis/>

## Installation

You can install the development version of bluelink like so:

``` r
remotes::install_github("mdsumner/bluelink")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(bluelink)
temp <- readRDS(system.file("extdata/ocean_temp.rds", package = "bluelink", mustWork = TRUE))


files <- tidyr::unnest(temp, cols = "bands") |> dplyr::filter(zlevel == 1)

files 
```


Now read through your chosen interface. 





```{r terra}
library(terra)
fs <- files |> dplyr::filter(date >= (max(date) - 5 * 24 * 3600))

## these are all the same file so we don't have to vectorize file to band
r <- rast(fs$dsn, lyrs = fs$band)
ex <- c(135, 155, -50, -30)
plot(crop(r, ext(ex)))

```

The system is pretty templated, so we can sub in a different variable. 

```{r sub}
u <- gsub("ocean_temp", "ocean_u", fs$dsn)
v <- gsub("ocean_temp", "ocean_v", fs$dsn)
u1 <- crop(rast(u, lyrs = fs$band), ext(ex))
v1 <- crop(rast(v, lyrs = fs$band), ext(ex))

plot(sqrt(u1^2 + v1^2), col = hcl.colors(26))

## the available vars generally come after "ocean_" but note there are others with a different pattern
branvariables <-
c("atm_flux_diag", "ice_force", "ocean_eta_t", "ocean_force",
"ocean_mld", "ocean_salt", "ocean_temp", "ocean_tx_trans_int_z",
"ocean_ty_trans_int_z", "ocean_u", "ocean_v", "ocean_w")


```

Go for depth. 

```{r depth}
zfiles <- tidyr::unnest(temp, cols = "bands") |> dplyr::filter(date == max(date))
idx <- as.integer(seq(1, 51, length.out = 12))
zfiles <- zfiles[idx, ]
## w too
u <- gsub("ocean_temp", "ocean_u", zfiles$dsn)
v <- gsub("ocean_temp", "ocean_v", zfiles$dsn)
#w <- vapour::vapour_vrt(, 
#                        extent = c(0.05, 360.05, -74.95,  75.05))
w <- gsub("ocean_temp", "ocean_w", zfiles$dsn)

u1 <- crop(rast(u, lyrs = zfiles$band), ext(ex))
v1 <- crop(rast(v, lyrs = zfiles$band), ext(ex))
w1 <- rast(w, lyrs = zfiles$band)
## w is offset to uv and temp because Arakawa-b
set.ext(w1, ext(rast(u[1], lyrs = 1)))
w1 <- crop(w1, ext(ex))

plot(sqrt(u1^2 + v1^2 + w1^2), col = hcl.colors(26))

#u1 <- vapour::vapour_warp_raster(zfiles$dsn[1], extent = ex, dimension = c(500, 500), bands = zfiles$band)

```


## Code of Conduct
  
Please note that the bluelink project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
